PANCHANGE_data_preprocessing

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected OCIR diff score

# Difference score for prepandemic and baseline ocir sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_prepan_base =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

>>>>

# Difference score for prepandemic and baseline ocir sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_base_prepan =
      as.numeric(
        ocir.sum_score_base - ocir.sum_score_prepan   # prepandemic sum score MINUS baseline sum score 
      )
  )
